---
title: "a sample flex dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: flatly
---

```{r setup, include=FALSE}
library(flexdashboard)
library(reactable)
library(tidyverse)
library(ggplot2)

theme_set(theme_minimal(15))

```


Sidebar Title {.sidebar}
==========================================

Using equal signs instead of dashes will place the sidebar globally. Global sidebar needs to come before the first page you have (iris in our case)


Your text here. You can use markdown syntax, including 
[links](http://blah.com), *italics*, **bolding**, etc.

Sidebar text here 

# iris {data-icon="fa-seedling"}

Column {.tabset data-width=650}
-----------------------------------------------------------------------

### Scatterplot

```{r, fig.width = 12, fig.cap = "Awesome Caption"}

ggplot(iris, aes(Sepal.Length, Sepal.Width)) +
  geom_point(aes(color = Species), size = 2) + 
  geom_smooth(color = "Purple", 
              fill = "Cornflowerblue") +
  scale_color_brewer(palette = "Dark2") + 
  theme(legend.position = "bottom")
  


#paleteer pacakage for all the plot palette collection 
```


### Table 

```{r}
reactable(iris)
```



Column {data-width=350}
-----------------------------------------------------------------------

### Bar chart

```{r}



iris %>% 
  group_by(Species) %>% 
  count(Species) %>% 
  mutate(Speies = fct_reorder(Species, n)) %>% 
  ggplot(aes(Species, n)) +
  geom_col() + 
  coord_flip()


```

iris %>% 
  group_by(Species) %>% 
  summarize(mean_sepal_length = mean(Sepal.Length)) %>% 
  ungroup() %>% 
  count(Species) %>% 
  mutate(Speies = fct_reorder(Species, mean_sepal_length)) %>% 
  ggplot(aes(Species, mean_sepal_length)) +
  geom_col() + 
  coord_flip()

# mtcars {data-icon="fa-car"}

Column {data-width =500}
-----------------------------------------------------------------------

### Scatterplot

```{r}
ggplot(mtcars, aes(disp, mpg)) + 
  geom_point(aes(color = factor(carb))) + 
  geom_smooth() + 
  theme(legend.position = "bottom") + 
  labs(x = "Engine Displacement", 
       y = "MPG") + 
  scale_color_brewer(palette = "Set2")
```


### Table 

```{r}
reactable(mtcars)
```


Column {data-width =500}
-----------------------------------------------------------------------

### Bar chart

```{r}
p <- mtcars %>% 
  rownames_to_column("car") %>% 
  as_tibble() %>% 
  group_by(cyl) %>% 
  summarize(mean_mpg = mean(mpg)) %>% 
  ggplot(aes(factor(cyl), mean_mpg)) +
  geom_col(aes(fill = "pink")) + 
  coord_flip()


plotly::ggplotly(p)

```

# more stuff {data-icon="fa-tree"}

